Output Summary

### 2023-03-13 03-post-process/output-plots-children/05-length-based-values.Rmd

  # function to create predicted survival curves for one posterior sample
  pred_fn = function(i) {
    pred_L_Pb = exp(omega0[i] + omega1[i] * E_scaled_seq)
    names(pred_L_Pb) = paste0("pred_L_Pb[", 1:30, "1]")
    pred_L_Pb
  }

>>>>

  # function to create predicted survival curves for one posterior sample
  pred_fn = function(i) {
    pred_L_Pb = exp(omega0[i] + omega1[i] * log(E_scaled_seq))
    names(pred_L_Pb) = paste0("pred_L_Pb[", 1:30, "1]")
    pred_L_Pb
  }
